Energy Efficiency for IoT Software in the Large \\ Progress Report

### 2018-08-11 Submissao/mid.tex
(>) mid evaluation

By the end of February was the submission deadline for \emph{LCTES'18}, the
main annual venue that links programming languages and embedded systems.
Fortunately, we had enough time to submit a full paper with the
proofs~\cite{ceu.lctes18} and a work-in-progress paper describing our approach
for transparent standby at the language level~\cite{ceu.lctes18.short}, both
of which were accepted for publication.
%
Even though we did not have a comprehensive evaluation of energy savings, the
conceptual framework and working prototype raised enough interest in the
community for discussion on the conference.

>>>>

By the end of February was the submission deadline for \emph{LCTES'18}, the
main annual venue that links programming languages and embedded systems.
Fortunately, we had enough time to submit a full paper with the
proofs~\cite{ceu.lctes18} and a work-in-progress paper describing our approach
for transparent standby at the language level~\cite{ceu.lctes18.short}, both
of which were accepted to the conference.
%
Even though we did not have a comprehensive evaluation of energy savings, the
conceptual framework and working prototype raised enough interest in the
community for discussion on the conference.
